The Exoplanet Orbit Database \textsc{II}: 2014 updates

### 2014-03-19 draft/ms.tex
abstract update

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The Exoplanet Orbit Database (EOD) is

We made an effort to put robustly detected exoplanets together with over 3000 sample of exoplanet candidates (\kepler\ Objects of Interest, KOIs) in the Exoplanet Orbit Database (EOD).

What does our  website go?
The EOD is available at exoplanets.org and we have ZZZ number of confirmed exoplanets as of March 2014.

What has been updated?

 Make sure to mention: data are available at exoplanets.org; KOIs are included.
ZZZ Also mention the number of confirmed planets? and maybe the scope of the EOD (what are in our database)

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The Exoplanet Orbit Database (EOD) collects orbital and stellar parameters of all known exoplanets reported in the peer-reviewed literature. The EOD can be navigated through the Exoplanet Data Explorer (EDE) Plotter and Table, available at exoplanets.org. We have ZZZ number of confirmed exoplanets as of March 2014. 
Since \cite{Wright2011}, we made an effort to put robustly detected exoplanets together with over 3000 sample of exoplanet candidates (\kepler\ Objects of Interest, KOIs) and other planets (the ones detected by microlensing, imaging, timing) on exoplanets.org. We also added some new fields (e.g. the secondary eclipse depths), removed obsolete fields, and revised some fields as necessary.

What  is the EOD?
What does our  website do?
What has been updated?
Make sure to mention: data are available at exoplanets.org; KOIs are included.
ZZZ Also mention the number of confirmed planets? and maybe the scope of the EOD (what are in our database)

@@

ZZZ orbital mass vs orbital distance

ZZZ screen shots of what it looks like in the browser

ZZZ add SE plots from Ming
